Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation

### 2024-12-03 paper/paper.qmd
Add files via upload

This survey data is titled About King St. Transit Pilot - Traffic & Pedestrian Volumes Summary and is available on Open Data Toronto at [https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/](https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/). It can be downloaded programmatically via the API, with example `R` code provided in the file "00-download_data.R".This dataset pertains to the King Street Transit Pilot, which commenced on November 12, 2017[@toronto_transit_data_2017,@toronto_king_street_proposal_2017a], and was implemented along King Street between Bathurst Street and Jarvis Street. The pilot aimed to prioritize streetcar traffic over private vehicles to improve transit reliability, speed, and capacity. The dataset provides monthly updates on traffic and pedestrian volumes recorded within the pilot area throughout the project, offering valuable data for analyzing the impacts of this transit initiative. It serves as a critical resource for evaluating the effectiveness of the pilot in optimizing urban transit and informing future city planning and transportation policies.

>>>>

This survey data is titled About King St. Transit Pilot - Traffic & Pedestrian Volumes Summary[@torontoKingSt] and is available on Open Data Toronto at [https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/](https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/). It can be downloaded programmatically via the API, with example `R` code provided in the file "00-download_data.R".This dataset pertains to the King Street Transit Pilot, which commenced on November 12, 2017[@toronto_transit_data_2017,@toronto_king_street_proposal_2017a], and was implemented along King Street between Bathurst Street and Jarvis Street. The pilot aimed to prioritize streetcar traffic over private vehicles to improve transit reliability, speed, and capacity. The dataset provides monthly updates on traffic and pedestrian volumes recorded within the pilot area throughout the project, offering valuable data for analyzing the impacts of this transit initiative. It serves as a critical resource for evaluating the effectiveness of the pilot in optimizing urban transit and informing future city planning and transportation policies.
